---
title: Assignment 3
author: Alex Moyse
output: 
  html_document:
    toc: true
    toc_float: true
---

<H1> Part 1 </H1>
Let's first start with loading libraries

```{r}
library(dplyr)
```

Once there, lets grab our raw data and import it into a dataframe with headers

```{r}
url.data <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"

raw <- read.csv(url(url.data), header = TRUE,)
```

Let's take a quick head of the data, and see what it looks like with headers

```{r}

head(raw)

```
<H2> Now let's filter! </h2>

We will now use grep to find things in the Majors column 
```{r}
majors<-rbind(raw[grepl("STATISTICS", raw$Major),], raw[grepl("DATA", raw$Major),])

head(majors)
```


<h1> Part 2 </h1>
<H2> The Novel Way </H2>
Let's start with grabbing Tidyverse, there will be conflits but that's outside of scope.
```{r}
library(tidyverse)
```

From there, let's grab our text file from in folder, and read it into a dataframe with a set deliminator. 


Looking at the character ", and then look for patterns. Clearly every even column has a valid entry. Proceed to filter the rows with only complete cases, IE not nulls, and then proceed to add them into the list. In this case we will have to ignore a parsing issue, due to the /r in the file. 

```{r}
file <- "Assignment_2_Text.txt"
df <- read_delim(file, delim='\"', col_names=FALSE, show_col_types = FALSE) 
list <- df$X2[complete.cases(df$X2)]
list <- (c(list, df$X4[complete.cases(df$X4)]))
list <- (c(list, df$X6[complete.cases(df$X6)]))
list <- (c(list, df$X8[complete.cases(df$X8)]))
print(sort(list))
```
<H2> The One Shot Regex Way </H2>

We are first going to import the string in a bit easier way, wrapping it with single quotes. This is because our data has double quotes, and this is th easiest way to adjust it to handle it. At this point we will also import the target output under the target variable. 

At this point we create a oneshot_extract with str_extract_all with a positive look behind, a search for up to two words, and then a positive look ahead. Practically this searches for between one and two words between two quotes.

```{r}
string_start <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'
target <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
oneshot_extract <- unlist(str_extract_all(string_start, "(?<=\")(\\w+.\\w+)(?=\")"))
target %in% oneshot_extract
oneshot_extract %in% target


```
In order to test this, we will use %in% first comparing the target to the extract to ensure that all of the values of the target are contained within the oneshot_extract. Now we will ensure that oneshot_extract does not have any values not contained within the target by reversing the comparison. With all of these results reading true, the exercise is complete. 

<H1> Part 3 </H1>

<H3> Part 3A </H3>

```{r}
test_case <- "(.)\1\1"
writeLines(test_case)
```

If we treat this as a parameter for a regex in r, it would be read as (.) with 2 invalid breakout characters. Parsed, through the r interpreter, it would look for any character, and be equal to "(.)". If we treat this as a language agnostic input, no language specific escape characters, it would be read as (.)\1\1, which matches 3 characters in a row. 


<H3> Part 3B </H3>
```{r}
test_case <- "(.)(.)\\2\\1"
writeLines(test_case)
```
Through the interpreter, it will be viewed as the output above. This would select the pattern of First Char Second Char then Second Char First Char
For example, 
  1. ABBA
  2. NIIN


<H3> Part 3C </H3>

```{r}
test_case1 <- "(..)\1"
writeLines(test_case1)
```
If we treat this as a parameter for a regex in r, it would be read as (..) with an invalid breakout character. Parsed, through the r interpreter, it would look for groups of 2 characters, and be equal to "(..)".


<H3> Part 3D </H3>

```{r}
test_case2 <- "(.).\\1.\\1"
writeLines(test_case2)
```
Sequence of 5 characters, 3 of the same separated by any two
For Example 
  1. ABACA
  
<H3> Part 3E </H3>

```{r}
test_case3 <- "(.)(.)(.).*\\3\\2\\1"
writeLines(test_case3)
```

Sequanece of 3 characters in order 123, any number of characters, then the same three characters in 321
For Example, 
  1. ABC***CBA

